Lens Modeling in \sw

### 2013-09-09 text/tex/results.tex
further work

We conclude that the volunteers are performing very well identifying and positioning images (T1a), with a performance of 92\% (approxPlace p=0.92).
Most of the problems where due to unclear arc-like structures (Error 1, p=0.18; Error 4, p=0.03; Error 8, p=0.04).
Critical failures like the failure to identify all fife images in an fife image system (Error 3, p=0.04) or to include too many images (Error 10, p=0.01) did almost never happend.
From this we conclude that the introduction materials was adequate and the volunteers got the basics of gravitational lensing.

@@

The ordering and assignment of minima / maxima / saddlepoint posed a more difficult task.
In p=59\% (N=70) of the cases the volunteers succeeded to identify the right configuration.
Most of the failures are due to error type 6 (PI/2), with N=38, p=32\%, followed by type 5 (PI) with N=7, p=6\%.
For an example of type 6 error, see \figref{6971}.

@@

In \figref{eR_all} can be seen, that the calculated einstein radius $\Theta_E$ of the models tend to be too high.
The overshoot varies from around 0.2 to 0.4 for for good models.
One of the reasons for this is, that it's hard to get the center of the lens on spot.
An offset leads to a a flatter mass profile for the model compared to the simulation.

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.80\textwidth]{fig/sims/eR_4.png}
  \caption{relative Einstein Radius for each model, per sim. }
  \label{fig:eR_all}
\end{figure}

Error 5 and 6 happen mostly in very symetric images, where it's hard to tell
It changes the orientation of the mass distribution.
But kappa encl and thus the einsteinradius is not changed, and thus the final result is still a valid model.

@@

Figure \ref{fig:6941} shows a simple example.

>>>>

We conclude that the volunteers are performing very well identifying and positioning images (T1a), with a performance of 92\% (approxPlace p=0.92).
Most of the problems where due to unclear arc-like structures (Error 1, p=0.18; Error 4, p=0.03; Error 8, p=0.04).
Critical failures like the failure to identify all fife images in an fife image system (Error 3, p=0.04) or to include too many images (Error 10, p=0.01) did almost never happened.
From this we conclude that the introduction materials was adequate and the volunteers understand the basics of gravitational lensing.

@@

The assignment of the parity of the images (T1b) posed a more difficult task.
In 59\% (rightOrder, p=0.59, N=70) of the cases the volunteers succeeded to identify the right configuration.
Most of the failures are due to Error 6 (PI/2), with N=38, p=32\%, followed by Error 5 (PI) with N=7, p=6\%.
For an example of type 6 error, see \figref{6971}.
While these errors occurred, we suspect they can be avoided with better training material and some examples for the obvious cases.
For more challenging cases, like very symmetrical distribution of the lensed images (for example model 6971, \figref{6971}), those errors should still produce plausible results, as will be explained in the next section.

@@

To compare the enclosed mass profile and the Einstein radius of the simulation and the models, \kenc was calculated using the mass map \kap[x,y] directly generated in the modeling process.
From the ensemble of models generated by one modelling process, the mean is taken as the resulting $\kappa(r)$ to calculate $\theta_E$.
To estimate the errors, also the extremal models are used to estimate a lower and upper limit for $\theta_E$.
These results can be seen in \figref{eR_all_models}.
This figure shows that this tecnique of esitmating the error is underestimating the error significantly and should be improved for further analysis.

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.80\textwidth]{fig/sims/eR_1.png}
  \caption{\tEr \gEr for all models with estimated erros in blue, \gEr of simulation in red}
  \label{fig:eR_all_models}
\end{figure}

In \figref{eR_per_sim} can be seen, that the calculated \tEr \gEr of the models tend to be too high.
The overshoot varies from around 0.2 to 0.4 for for good models.
One of the reasons for this is, that it's hard to get the center of the lens on spot.
An offset leads to a a flatter mass profile for the model compared to the simulation.

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.80\textwidth]{fig/sims/eR_4.png}
  \caption{relative Einstein Radius for each model, per sim. }
  \label{fig:eR_per_sim}
\end{figure}

Error 5 and 6 happen mostly in very symmetric images, where it's hard to tell
It changes the orientation of the mass distribution \kap[x,y].
But \kenc and thus the \tEr \gEr is not changed, and thus the final result is still a valid model.
This can be easily corrected, if further analysis is done for the modeled system and time delays are known.

@@

\todo{incl this figs}
Figure \ref{fig:6941} shows a simple example.
